### 2016-02-08 ch05-initvals/InitialValuesPaper.tex
Init-vals: more or less ready

The main aim and contribution of this article is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
Hence, such techniques make it possible to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
%Such techniques, hence allow to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.

@@

In this chapter, the Clopper-Pearson method--as implemented in \MATLAB's \code{binofit}-- is used whenever confidence bounds are shown.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly due to the conservatism in these bounds.
However, since there is often a clear separation between the different techniques, no efforts have been made to use confidence interval estimators that offer less conservative results.

>>>>

The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
Hence, such techniques make it possible to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
%Such techniques, hence allow to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.

@@

In this chapter, the Clopper-Pearson method---as implemented in \MATLAB's \code{binofit}---is used whenever confidence bounds are shown.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly due to the conservatism in these bounds.
However, since there is often a clear separation between the different techniques, no efforts have been made to use confidence interval estimators that offer less conservative results.

### 2016-02-08 ch05-initvals/letter.inc.tex
Init-vals: more or less ready

\newcommand{\reviewer}[1]{\paragraph{#1}}

\begin{quote}

The use of a fixed method would greatly simplify an algorithm design in any standalone autonomous toolbox. The results in Table II do not help to uncover whether such a strategy is permissible. To solve this dilemma, two histograms of differences $\Delta = \model{best} - \model{2nd}$ need to be built and shown: one for $\model{best} = \model{FRIR}$ and the other for $\model{best} \neq \model{FRIR}$.
\end{quote}

We agree that a single method would greatly simplify the implementation of a toolbox.
However, we think that using multiple initial value strategies is a valuable approach since this makes a toolbox more robust to different conditions (SNR, frequency resolution, system order, \ldots) as it reduces the likelihood that a local optimum is hit.
This can e.g. be seen in subplot 2 of \figref{fig:distancesStress} (which is discussed further on).
A similar approach w.r.t. to combine initial values is followed in some toolboxes, e.g. \cite{FDIDENT,TDIDENT}.

Many nature-inspired optimization algorithms (such as Particle Swarm Optimization (PSO)) and stochastic optimization algorithms even use hundreds or thousands of randomized initial values, in part to avoid local optima.
But, obviously, using many initial values comes at a (considerable) increase in computational cost.

While this discussion and this inherent trade-off is very interesting, we think this is outside of the scope of the paper where we only wish to demonstrate that smoothing techniques such as RFIR are a worthwhile source of initial values, but not necessarily the only one.

>>>>

% \begin{quote}

% The use of a fixed method would greatly simplify an algorithm design in any standalone autonomous toolbox. The results in Table II do not help to uncover whether such a strategy is permissible. To solve this dilemma, two histograms of differences $\Delta = \model{best} - \model{2nd}$ need to be built and shown: one for $\model{best} = \model{FRIR}$ and the other for $\model{best} \neq \model{FRIR}$.
% \end{quote}

% We agree that a single method would greatly simplify the implementation of a toolbox.
% However, we think that using multiple initial value strategies is a valuable approach since this makes a toolbox more robust to different conditions (SNR, frequency resolution, system order, \ldots) as it reduces the likelihood that a local optimum is hit.
% This can e.g. be seen in subplot 2 of \figref{fig:distancesStress} (which is discussed further on).
% A similar approach w.r.t. to combine initial values is followed in some toolboxes, e.g. \cite{FDIDENT,TDIDENT}.

% Many nature-inspired optimization algorithms (such as Particle Swarm Optimization (PSO)) and stochastic optimization algorithms even use hundreds or thousands of randomized initial values, in part to avoid local optima.
% But, obviously, using many initial values comes at a (considerable) increase in computational cost.

% While this discussion and this inherent trade-off is very interesting, we think this is outside of the scope of the paper where we only wish to demonstrate that smoothing techniques such as RFIR are a worthwhile source of initial values, but not necessarily the only one.
